 

### 2020-12-04 doc/manuscript/tables_figures/tables.Rmd
add species code to species table
needed for interpretation of tree-ring figure

#36

\newpage
```{r species_table, eval=TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
species_table <- read.csv(file = "species_table.csv", col.names = c("site", "xylem porosity","species","n trees", "n tree-years", "n cores", "date range"),  stringsAsFactors = FALSE, check.names = FALSE)
kable(species_table, caption = "Table 2. Dominant ring- and diffuse-porous species at SCBI and Harvard Forest analyzed here, along with sample sizes.",  format = "latex", booktabs = TRUE,  escape = F) %>%
add_header_above(c(" ", " ", " ", "Dendrometer Bands" = 2, "Tree Cores"=2 )) %>%
kable_styling(latex_options = c("scale_down", "hold_position"), protect_latex = T) 
```

>>>>

\newpage
```{r species_table, eval=TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
species_table <- read.csv(file = "species_table.csv", col.names = c("site", "xylem porosity","species", "species code", "n trees", "n tree-years", "n cores", "date range"),  stringsAsFactors = FALSE, check.names = FALSE)
kable(species_table, caption = "Table 2. Dominant ring- and diffuse-porous species at SCBI and Harvard Forest analyzed here, along with sample sizes.",  format = "latex", booktabs = TRUE,  escape = F) %>%
add_header_above(c(" ", " ", " ", " ", "dendrometer bands" = 2, "tree cores"=2 )) %>%
kable_styling(latex_options = c("scale_down", "hold_position"), protect_latex = T) 
```
